---
title: "Visualizing US Phillips Curves, 1948 to 2016"
author: "Andy Harless"
date: "3/23/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

***

Do policymakers face a tradeoff between unemployment and inflation?  And in what sense?

It's a complicated question with many ramifications, and I won't attempt a convincing answer.  But it helps to be able to visualize the data in a flexible way.

This app gives you that ability.

***
Annual US data 1956-1969 show the classic inverse relation
```{r echo=TRUE}
u = c(4.1,4.3,6.8,5.5,5.5,6.7,5.6,5.6,5.1,4.5,3.8,3.8,3.6,3.5)
i = c(2.9,2.9,1.7,1.7,1.4,0.7,1.3,1.6,1.0,1.9,3.4,3.0,4.6,6.0)
plot(u, i, xlab="Unemployment", ylab="Inflaiton")
```

***
But 1967-1981 show how the relation (famously) failed
```{r echo=TRUE}
u = c(3.8,3.6,3.5,5.0,6.0,5.6,4.9,5.6,8.5,7.7,7.1,6.1,5.9,7.1,7.6)
i = c(3.0,4.6,6.0,5.4,3.2,3.3,8.3,11.7,6.7,4.8,6.5,8.6,12.5,11.8,8.5)
plot(u, i, xlab="Unemployment", ylab="Inflaiton")
```

***
Using monthly US data, my app lets you see the big picture while focusing on interesting details.

- See how the US unemployment and inflation time series evolved from 1948 to 2016

- Choose subperiods to look at more closely

- Make scatterplots

- Vary the appearance of scatterplots to get a better idea of what's really happening

- Summarize the data with linear or quadratic fits